---
title: "VideoGameSales"
author: "amanda, ben, and viv"
output: 
  html_document:
    df_print: paged
    toc: yes
    toc_depth: '3'
    toc_float: yes
---

```{r, eval=TRUE, include=FALSE}

knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)

library(tidyverse)
library(ggplot2)
library(plotly)


project.dir <- getwd()
dataset.dir <- "data"
outputs.dir <- "output"
```

# Data Import and Cleaning

## Data Import
```{r}
videogames.df <- read.csv(file.path(project.dir, dataset.dir, 'vgsales-12-4-2019.csv'))
colnames(videogames.df)
```

## Data cleaning
Since 
```{r}
videogames.clean <- videogames.df %>% filter(Year < 2019)
```


# 1. {.tabset}

Conduct some descriptive analysis on the data, figuring out:
•distributions of variables,
•variables that appear to be strongly related with each other (using appropriate methods to quantify the relationships based on whether variables are numerical or categorical).

## Global Sales
From the boxplot we can see that we have 2 extreme outliers. After investigating, it looks like two outliers are the for GTA V (ps3 and ps4)
```{r}
hist(videogames.clean$Global_Sales, xlab = 'Global Sales (millions of USD)')

hist(videogames.clean$Global_Sales,
     xlab = 'Global Sales (millions of USD)',
     xlim = c(0, .5),
     breaks = 10000)

boxplot(videogames.clean$Global_Sales, xlab = 'Global Sales (millions of USD)')
videogames.clean[which(videogames.clean$Global_Sales > 17), ]
```

```{r}
vs.byyear <- videogames.df %>% 
  group_by(Year) %>%
  summarise(GlobalSales = sum(Global_Sales, na.rm = T),.groups = 'drop' )

plot(x = vs.byyear$Year, y=vs.byyear$GlobalSales)
```

